---
title: "Basic Exploratory Analysis"
author: "TARUN"
date: "26/08/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The goal of this project is just to display that you've gotten used to working with the data and that you are on track to create your prediction algorithm. Please submit a report on R Pubs (http://rpubs.com/) that explains your exploratory analysis and your goals for the eventual app and algorithm. This document should be concise and explain only the major features of the data you have identified and briefly summarize your plans for creating the prediction algorithm and Shiny app in a way that would be understandable to a non-data scientist manager. You should make use of tables and plots to illustrate important summaries of the data set. The motivation for this project is to: 1. Demonstrate that you've downloaded the data and have successfully loaded it in.2. Create a basic report of summary statistics about the data sets.3. Report any interesting findings that you amassed so far.4. Get feedback on your plans for creating a prediction algorithm and Shiny app.

```{r message=FALSE,warning=FALSE}
library(ggplot2)
library(dplyr)
library(tokenizers)
library(stringi)
library(stringr)
library(tm)
library(quanteda)
```

## Downloading Data

```{r echo=TRUE}
if(!file.exists("./Coursera-SwiftKey")){
  dir.create("./data")
  url <- "https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip"
  download.file(Url, destfile="./data/Coursera-SwiftKey.zip", mode = "wb")
  unzip(zipfile="./data/Coursera-SwiftKey.zip", exdir="./data")
}
```

##Reading Data
```{r echo=TRUE,message=FALSE,warning=FALSE}
datablog <- readLines("./Coursera-SwiftKey/final/en_US/en_US.blogs.txt")
datanews <- readLines("./Coursera-SwiftKey/final/en_US/en_US.news.txt")
datatwitter <- readLines("./Coursera-SwiftKey/final/en_US/en_US.twitter.txt")

##summary of data
stri_stats_general(datablog)
stri_stats_general(datanews)
stri_stats_general(datatwitter)

```

##Creating Data

```{r message=FALSE,warning=FALSE}
subblog <- sample(datablog,size = 1000)
subnews <- sample(datanews,size = 1000)
subtwitter <- sample(datatwitter,size = 1000)
sampledData <- c(subblog,subnews,subtwitter)
head(sampledData)
corpora <- VCorpus(VectorSource(sampledData))
```

##Transforming Data

```{R}
toSpace <- content_transformer(function(x, pattern) gsub(pattern, " ", x))
corpora <- tm_map(corpora, toSpace, "/|@|//|$|:|:)|*|&|!|?|_|-|#|¦|€|â|™|ã|$")
corpora <- tm_map(corpora,content_transformer(tolower))
corpora <- tm_map(corpora,removePunctuation)
corpora <- tm_map(corpora,stemDocument)
corpora <- tm_map(corpora,stripWhitespace)
corpora <- tm_map(corpora,removeWords,stopwords("english"))
corpora <- tm_map(corpora,removeNumbers)
corpora <- tm_map(corpora,stripWhitespace)
```

##Data Exploration

```{r}
dtm1 <- TermDocumentMatrix(corpora)
freq <- apply(as.matrix(dtm1),1,sum)
freq <- sort(freq,decreasing = TRUE)
freqdf <- data.frame(words = names(freq),frequency = freq)
## Plot to see distribution of words
ggplot(freqdf[1:25,],aes(words,frequency)) +
  geom_bar(stat = "identity",fill = "blue",color = "blue") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))


## Now lets try 2 gram model
corpora <- corpus(corpora)
tk <- tokens(corpora)
tk1 <- tokens_ngrams(tk)
dfm1 <- dfm(tk1)
bifreq <- colSums(dfm1)
bifreq <- sort(bifreq,decreasing = TRUE)
bifreqdf <- data.frame(bigram = names(bifreq),frequecy = bifreq)

ggplot(bifreqdf[1:25,],aes(bigram,frequecy)) +
  geom_bar(stat = "identity",fill = "blue",color = "blue") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))

## Now lets try 3 gram model
tk2 <- tokens_ngrams(tk,3)
dfm2 <- dfm(tk2)
trifreq <- colSums(dfm2)
trifreq <- sort(trifreq,decreasing = TRUE)
trifreqdf <- data.frame(trigram = names(trifreq),frequecy = trifreq)

ggplot(trifreqdf[1:25,],aes(trigram,frequecy)) +
  geom_bar(stat = "identity",fill = "blue",color = "blue") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))

## lets look at a word graph 
textplot_wordcloud(dfm1,max_words = 20,color = RColorBrewer::brewer.pal(8,"Dark2"))
```

## Future plans

```{r}
#Planning to create a model using 2 gram and 3 gram models and coming up with a
#effective ml algorithm in a way it predicts with great accuracy.
```
